Stock enhancement undermines ecological stability

### 2022-02-23 rmd/manuscript.Rmd
edit: manuscript

---
title: "Stock enhancement undermines ecological stability"
output:
  pdf_document:
    latex_engine: xelatex
#  word_document:
#    reference_docx: word_format.docx
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
---

@@

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Masato Yamamichi for helpful discussion on this manuscript. Data and codes will be made available upon acceptance.

>>>>

---
title: "Stock enhancement undermines ecological stability"
output:
  pdf_document:
    latex_engine: xelatex
#  word_document:
#    reference_docx: word_format.docx
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

We are grateful to people involved in the long-term monitoring program at the protected watersheds in Hokkaido. We thank Masato Yamamichi for helpful discussion on this manuscript. Data and codes are available at <https://github.com/aterui/public-proj_fishery-stability>.
